### 2020-12-16 Thesis-Chapter2-Background.tex
Editorial improvements

The primary judiciary function is to adjudicate the law through the determination of facts and interpretation of
authoritative legal texts. However, whether it is contested, conceded, condemned, or condoned, the judicial branch also
establishes legal doctrine and actively enforces rulings in a manner that amounts to creation of public policy
\cite{feeley_judicial_2000}. Due to Congress's clear authority over telecommunications and federal investigatory powers,
the courts are most likely to exert influence in this area through interpretation of current law. This interpretation
will both determine how present law is enforced and draw constitutional boundaries around any actions the executive or
legislative branches undertake.

>>>>

The primary judiciary function is to adjudicate the law through the determination of facts and interpretation of
authoritative legal texts. However, whether it is contested or conceded, condemned or condoned, the judicial branch also
establishes legal doctrine and actively enforces rulings in a manner that amounts to creation of public policy
\cite{feeley_judicial_2000}. Due to Congress's clear authority over telecommunications and federal investigatory powers,
the courts are most likely to exert influence in this area through interpretation of current law. This interpretation
will both determine how present law is enforced and draw constitutional boundaries around any actions the executive or
legislative branches undertake.
